\plaintitle

### 2017-05-22 papers/IoT2017/paper.tex
no message

\begin{figure*}[h]
\center
\begin{tikzpicture}[x=3.5cm, y=2cm, font=\small,
  system/.style={draw, align=center, rounded corners=0.1cm, fill=black!5},
  entity/.style={draw, align=center, rounded corners=0.1cm},
  asset/.style={midway, align=center},
  transfer/.style={->, >=stealth, shorten <=0.05cm, shorten >=0.05cm},
]
\node[entity] (smartmeter) at (0, 1) {smart\\meter};
\node[entity] (prosumer1) at (1, 1) {prosumer};
\node[system] (mixing1) at (2, 1) {mixing\\service};
\node[entity] (prosumer2) at (3, 1) {prosumer\\(alternative ID)};
\node[system] (bidstorage) at (4, 1) {bid\\storage};
\node[entity] (partner) at (4, 0) {other prosumer};
\node[entity] (prosumer3) at (3, 0) {prosumer\\(alternative ID)};
\node[system] (mixing2) at (2, 0) {mixing\\service};
\node[entity] (prosumer4) at (1, 0) {prosumer\\(second alternative ID)};

\draw[transfer] (smartmeter) -- node [asset, above] {energy\\asset} (prosumer1);
\draw[transfer] (prosumer1) -- node [asset, above] {energy\\asset} (mixing1);
\draw[transfer] (mixing1) -- node [asset, above] {energy\\asset} (prosumer2);
\draw[transfer, dashed] (prosumer2) -- node [asset, above] {sell\\bid} (bidstorage);
\draw[transfer, dashed] (bidstorage) -- node [asset, right] {sell\\bid} (partner);
\draw[transfer, bend right] (partner) to node [asset, below] {financial\\asset} (prosumer3);
\draw[transfer] (prosumer2) -- node [asset, above right] {energy\\asset} (partner);
\draw[transfer] (prosumer3) -- node [asset, below] {financial\\asset} (mixing2);
\draw[transfer] (mixing2) -- node [asset, below] {financial\\asset} (prosumer4);
\draw[transfer] (prosumer4) -- node [asset, below left] {financial\\asset} (smartmeter);
\end{tikzpicture}
\caption{Simplified overview of transactions for selling energy. Note that in order to prevent de-anonymization, a prosumer should use multiple addresses for mixing.}
\end{figure*}

@@

We may achieve this goal using multiple approaches for blockchain transaction anonymity:
\begin{itemize}
\item Mixing services (also known as tumblers) mix potentially identifiable assets on a blockchain with others, thereby preventing tracing individual assets back to their original source. 
In our case, assets to be mixed can include virtual balances of both fiat currencies and energy.
\item Cryptographic anonymity for transactions is provided, for example, by Zerocoin~\cite{miers2013zerocoin}. Similarly to mixing service, Zerocoin can prevent tracing assets on a blockchain.
\end{itemize}
Using the above techniques, we can enable prosumers to trade energy anonymously (i.e., without revealing their true identities), but at the same time prevent them from altering their energy or financial balances without a valid transaction.

However,

>>>>

\begin{figure*}[h]
\center
\begin{tikzpicture}[x=4.15cm, y=2cm, font=\small,
  system/.style={draw, align=center, rounded corners=0.1cm, fill=black!5},
  entity/.style={draw, align=center, rounded corners=0.1cm},
  asset/.style={midway, align=center},
  transfer/.style={->, >=stealth, shorten <=0.05cm, shorten >=0.05cm},
]
\node[entity] (smartmeter) at (0, 1) {smart\\meter};
\node[entity] (prosumer1) at (1, 1) {prosumer};
\node[system] (mixing1) at (2, 1) {mixing\\service};
\node[entity] (prosumer2) at (3, 1) {prosumer\\(alternative ID)};
\node[system] (bidstorage) at (4, 1) {bid\\storage};
\node[entity] (partner) at (4, 0) {other prosumer};
\node[entity] (prosumer3) at (3, 0) {prosumer\\(alternative ID)};
\node[system] (mixing2) at (2, 0) {mixing\\service};
\node[entity] (prosumer4) at (1, 0) {prosumer\\(second alternative ID)};

\draw[transfer] (smartmeter) -- node [asset, above] {energy\\production asset} (prosumer1);
\draw[transfer] (prosumer1) -- node [asset, above] {energy\\production asset} (mixing1);
\draw[transfer] (mixing1) -- node [asset, above] {energy\\production asset} (prosumer2);
\draw[transfer, dashed] (prosumer2) -- node [asset, above] {energy production asset,\\sell bid} (bidstorage);
\draw[transfer, dashed] (bidstorage) -- node [asset, right] {sell\\bid} (partner);
\draw[transfer, bend right=15] (partner) to node [asset, below] {financial asset,\\energy\\consumption asset} (prosumer3);
\draw[transfer, bend right=7.5] (prosumer2) to node [asset, above right] {energy\\prod. asset} (partner);
\draw[transfer] (prosumer3) -- node [asset, below] {financial asset,\\
energy consumption asset} (mixing2);
\draw[transfer] (mixing2) -- node [asset, below] {financial asset,\\energy consumption asset} (prosumer4);
\draw[transfer] (prosumer4) -- node [asset, below left] {financial\\asset} (smartmeter);
\end{tikzpicture}
\caption{Simplified overview of transactions for selling energy. Note that in order to prevent de-anonymization, a prosumer should use multiple addresses for mixing and multiple rounds of mixing.}
\end{figure*}

@@

We may achieve this goal using multiple approaches for blockchain transaction anonymity:
\begin{itemize}
\item Mixing services (also known as tumblers) mix potentially identifiable assets on a blockchain with others, thereby preventing tracing individual assets back to their original source. 
In our case, assets to be mixed include virtual balances of fiat currencies as well as energy production and consumption.
\item Cryptographic anonymity for transactions is provided, for example, by Zerocoin~\cite{miers2013zerocoin}. Similarly to mixing service, Zerocoin can prevent tracing assets on a blockchain.
\end{itemize}
Using the above techniques, we can enable prosumers to trade energy anonymously (i.e., without revealing their true identities), but at the same time prevent them from altering their energy or financial balances without a valid transaction.

However, we must also ensure that 1) smart meters know the amount of energy purchased or sold by their prosumer and 2) prosumers cannot purchase or sell more energy than their capacity.
To satisfy both of these constraints, all energy trades must start with the prosumer withdrawing a certain amount of energy production or consumption from its smart meter:
\begin{itemize}
\item If a prosumer wishes to sell energy, it must first obtain an energy asset from its smart meter using a blockchain transaction.
This transaction must be signed by the smart meter, which enables the smart meter to 1) keep track of the amount of energy traded by the prosumer as well as to 2) enforce safety requirements by limiting the amount of energy that can be withdrawn.
\item If a prosumer wishes to buy energy, it must first obtain an energy consumption asset from its smart meter in a way similar to obtaining an energy production asset.
\end{itemize}
